---
title: "University of Alberta Faculty of Engineering Research Metrics"
author: "Alison Henry"
date: "January 18, 2018"
output: word_document
        df_print: kable
bibliography: 2018ROA.bib
csl: chemical-engineering-journal.csl
params:
        dataLoc:
                label: "Location of data files"
                value: https://drive.google.com/drive/folders/0BzuuY7vK5mRBTmtXeFQ4RDVIYXM?usp=sharing
                input: text
        dataSource:
                label: "Data Source"
                value: Scopus
                input: select
                choices: [Scopus, "Web of Science"]
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
A report to examine the publication output of the Univeristy of Alberta Faculty of Engineering. Searches were conducted using `, and limited to the five publication years from 2012-2016.

```{r package installation}
##Install and load needed packages

##install.packages("bibliometrix", dependencies = TRUE)
##install.packages("splitstackshape")
##install.packages("tidyverse")
##install.packages("viridis")
##install.packages("knitr")

library (googledrive)
library(bibliometrix)
library(splitstackshape)
library(tidyverse)
library(stringr)
library(viridis)
library(knitr)
```

Initial processing of the data was accomplished with the Bibliometrix package written by Massimo Aria and Corrado Cuccurullo[@RefWorks:doc:59d24e48e4b0b590b97a2290]. This allowed easy conversion of records into a data frame to facilitate further processing.

```{r read in bibtex files} 
## Read in downloaded files and convert to dataframe
filePaths <- dir("./WoSdata", pattern = "*.bib", recursive = TRUE, full.names = TRUE) 
D <- do.call("readFiles", as.list(filePaths)) 
M <- convert2df(D, dbsource = "isi", format = "bibtex")
```
