---
title: "University of Alberta Faculty of Engineering Research Metrics"
author: "Alison Henry"
date: "February 13, 2018"
output: word_document
##        df_print: kable
##bibliography: 2018ROA.bib
##csl: chemical-engineering-journal.csl
##params:
##        dataLoc:
##              label: "Location of data files"
##                value: "./data"
##                input: text
##        dataSource:
##                label: "Data Source"
##                value: Scopus
##                input: select
##                choices: [Scopus, "Web of Science"]
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, include = FALSE)
```
A report to examine the publication output of the Univeristy of Alberta Faculty of Engineering. Searches were conducted using `, and limited to the five publication years from 2012-2016.

```{r package installation}
##Install and load needed packages

##install.packages("bibliometrix", dependencies = TRUE)
##install.packages("splitstackshape")
##install.packages("tidyverse")
##install.packages("viridis")
##install.packages("knitr")

library(bibliometrix)
library(tidyverse)
library(stringr)
library(viridis)
library(knitr)
```

Initial processing of the data was accomplished with the Bibliometrix package written by Massimo Aria and Corrado Cuccurullo[@RefWorks:doc:59d24e48e4b0b590b97a2290]. This allowed easy conversion of records into a data frame to facilitate further processing.

```{r read in bibtex files} 
## Read in downloaded files and convert to dataframe
filePaths <- dir("./data", pattern = "*.bib", recursive = TRUE, full.names = TRUE) 
D <- do.call("readFiles", as.list(filePaths)) 
M <- convert2df(D, dbsource = "scopus", format = "bibtex")

##files <- drive_ls(path == params$dataLoc)
##apply(files, 1, drive_download)
```

```{r run biblioAnalysis}
result<-biblioAnalysis(M)
```

##International Collaborations
```{r Countries, results=asis}
# Create a country collaboration network
M <- metaTagExtraction(M, Field = "AU_CO", sep = ";")
NetMatrix <- biblioNetwork(M, analysis = "collaboration", network = "countries", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, n = dim(NetMatrix)[1], Title = "Country Collaboration", type = "circle", size=TRUE, remove.multiple=FALSE,labelsize=0.8)
net
```